\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{Barbie RPG instruction manual}

\author{Alex Nguyen}

\date{\today}

\begin{document}
\maketitle

\section{Story}
Barbie and co fight with Raquelle. Be creative and create your own adventure
\section{Instructions}
All four characters start off with their max Hp of 8000. In general all 4 characters have 4 options they can do each turn; they can attack normally, consume Mp to perform one of two special attacks that are unique to each character, or they can do nothing. Please note that the commands MUST BE TYPED EXACTLY THE SAME WAY THEY ARE SPELLED IN THE SUBSUBSECTION TITLES
\subsection{Barbie's turn}
During Barbie's turn she has the following options:
\subsubsection{attack}
Barbie does a normal attack. Barbie has the second weakest attack.
\subsubsection{fragrance storm}
Barbie sprays the whole party with perfume to cause everyone to recover a moderate amount of health. It cost 30 Mp
\subsubsection{pet fury}
Barbie summons her pet cat Blissa, her pet dog Taffy, and her pet horse Tawny to attack Racquelle. This is the strongest attack out of all the four main characters. It cost 35 Mp.
\subsubsection{do nothing}
Barbie does nothing
\subsection{Ken's turn}
During Ken's turn he has the following options:
\subsubsection{attack}
Ken does a normal attack. He has the weakest of all the normal attacks
\subsubsection{unswoon}
Ken revives someone who is at 0 hp. Note that Ken can't revive himself so if he becomes swooned you can't revive anyone else for the rest of the game. This ability cost 30 Mp.
\subsubsection{macho defense}
Ken shows off his muscles distracting Raquelle making her next attack less effective. This cost 15 Mp.
\subsubsection{do nothing}
Ken does nothing
\subsection{Nikki's turn}
\subsubsection{attack}
Nikki physically attacks. She has the strongest normal attack in the game. 
\subsubsection{bend and snap DJ}
She starts playing some jamming tunes that increases everyone's damage starting on Barbie's next move. This ability cost 15 Mp
\subsubsection{makeover}
Nikki gives someone a makeover recovering their health. Telling her who to target isn't case sensitive, the acceptable things you can tell her are Barbie, barbie, Ken, ken, Nikki, nikki, Ryan, and ryan. This ability cost 10 Mp 
\subsubsection{do nothing}
Nikki doesn't do anything.
\subsection{Ryan's turn}
\subsubsection{attack}
Ryan attacks. He has the second highest physical attack in the game
\subsubsection{jam out}
Ryan jams out on his guitar causing everyone to recover 20 Mp (except himself). This ability cost 35 Mp.
\subsubsection{serenade}
Ryan serenades and tries to impress Barbie causing him to regain 40 Mp. This ability cost 1 Mp to use. Note that Ryan needs atleast one Mp to use this ability so Ryan ever runs out of Mp you have no way to restore the Mp of your other characters. 
\subsubsection{do nothing}
Ryan does nothing.
\end{document}